---
title: "STV2022 Tasks"
author: "Gard Olav Dietrichson"
date: '2022-09-02'
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(stortingscrape)
library(tidyverse)
library(tidytext)
library(quanteda)
library(stm)
library(tidyr)
library(viridis)
library(rvest)
library(xml2)
library(httr)

```

## Tasks to be answered in the first seminar

### Note down a Hypothesis based on existing theories

The literature on political representation, and particularly that of women's representation make a distinction between what is known as descriptive and substantive representation (CITE). While there are other types of representation discussed in political science (Pitkin, 1967), these are the ones that capture most of the active research currently. The distinction between these forms can be summed up as focusing on who legislators *are* and what they *do*. The highly active field is also ripe with the debate on the relation between these two, as some claim that descriptive representation is in fact a necessity in order to ensure substantive represention of minorities' interests (Phillips, 1995).

With my semester task I wish to test whether women representatives in the Norwegian parliament are the central actors that bring about the substantive representation of women, or whether they are simply in line with the party focus. To that end I wish to study the individual speech acts of members of the Norwegian parliament, and discuss how patterns of questions regarding women's issues, and issues that affect women, come about. Who asks these questions? When and Why?. And how does the government constellation affect these patterns, given that around 90% of all questions are asked by opposition politicians?


### Find a Datasource that you imagine could be used to answer your hypothesis

Fortunately, these data are easy to find, as the storting has a publicly available API for usage. Even more fortunately, the eminent political scientist Dr. Martin Søyland has created a R-package for easier use of that API. I take advantage of those functions in order to retrieve all the questions that I can get my hands on. However, it should be noted that the API only has data back to 1996, leaving us somewhat wanting in terms of data in the early days of the storting, when a more male dominated storting was present, and women's issues were likely to be viewed with a more consverative bent. However, the data still covers a series of periods coinciding with a different set of government coalitions. It covers 9 different government coalitions, including Jagland, Bondevik I, Stoltenberg I, Bondevik II, Stoltenberg II, Solberg I, Solberg II, Solberg III, and Solberg IV, and Støre I. This includes then several periods of both socialist block government, and socialist block government, and will hopefully help illuminate some of the differences that party and incumbent government can have on MP's furtherance of women's issues in parlimant.

### Retrieve and Structure Data

The following code chunks were used to retrieve data. Preliminarily I know that the stortings API only covers questions from current session back to the 1996-1997 session. As such I start by limiting the sessions that I can aquire data for. 

```{r, eval=FALSE}
## Retrieving the Sessions that I know I can get data on
sessions <- get_parlsessions()

sessions <- sessions %>% 
  filter(!(id %in% c("2022-2023", "2023-2024", "2024-2025", 
                     "1995-96", "1994-95", "1993-94",
                     "1992-93", "1991-92", "1990-91", "1989-90",
                     "1988-89", "1987-88", "1986-87")))

```

This creates a set of sessions that I will use later as well, in order to merge this with important data on the mp's, the people who make statements. The next step is then to use the API functions of the storting to retrieve the meta-data of all the questions asked in each session.

```{r}
a <- list()
b <- list()
c <- list()

for(x in unique(sessions$id)){
  it <- 100*(which(unique(sessions$id) == x)/length(unique(sessions$id)))
  cat(paste0(sprintf("Progress: %.4f%%             ", it), "\r"))
  
  a[[x]] <- get_session_questions(sessionid = x, 
                                  q_type = "interpellasjoner", 
                                  status = NA,
                                  good_manners = 0)
  b[[x]] <- get_session_questions(sessionid = x, 
                                  q_type = "sporretimesporsmal",
                                  status = NA,
                                  good_manners = 0)
  try(c[[x]] <- get_session_questions(sessionid = x,
                                  q_type = "skriftligesporsmal",
                                  status = NA,
                                  good_manners = 0))
}

aex <- do.call("rbind", a)
bex <- do.call("rbind", b)
cex <- do.call("rbind", c)

dlist <- list(aex, bex, cex)

questionsmeta <- do.call("rbind", dlist)

rm(aex, bex, cex, dlist)
```

We now have a dataframe which contains all the meta info on the questions, meaning who asked the question, when it was asked, the topic and who answered it. But to get the exact text of the question itself we have to retrieve that individually. The API allows us to extract individual text of questions through the relevant id variable, which gives a unique id to the questions asked. By running a loop over the meta info we have, we can create a new list of the exact information of all these questions. Fair bit of warning, this takes time, especially if you want to be nice to the poor storting servers, and include some $Sys.sleep$ between each request. 1 sec sleep on the integer means that scraping will take 51 000 seconds, or 14 hours.  

```{r, eval=FALSE}
d <- list()

for(x in unique(questionsmeta$id)){
  it <- 100*(which(unique(questionsmeta$id) == x) / length(unique(questionsmeta$id)))
  cat(paste0(sprintf("Progress: %.4f%%             ", it), "\r"))
  
  try(d[[x]] <- get_question(questionid = x, good_manners = 1))
}


questiontext <- do.call("rbind", d)

save(questiontext, file = "data/questiontext.Rdata")
```

Note that there are approximately 112 observations not in the finished retrieved dataset. I check the causes and double check why they are missing under.

```{r}
checks <- questionsmeta %>% 
  filter(!(questionsmeta$id %in% questiontext$id))

save(checks, file = "data/outliers.Rdata")

```

I manually apply some of the quesiond id's to the retrieval creator at the storting's homepage. A double check confirms that these are indeed empty documents that are returned.

```{r}
table(checks$session_id)
```
The quick check demonstrates that most of the missing ones are from 2018-2019, and the remaining are relatively evenly spread out. At first glance there appears to be nothing that unifies these missing ones, as they seem to have a relatively even spread of topics that they cover. I presume as of now, that these questions will not be relevant to my research.

I move on to the next step which is joining the full dataset with the important data that I wish to use for independent variables, that of MP characteristics. The dataset of full questions at the moment, contains no mentions of precise MP characteristics, as such I have to return to the API through the stortingscrape package, and retrieve this information through a different set of steps. 

```{r}
periods_storting <- get_parlperiods()

periods_storting <- periods_storting %>%
  filter(id %in% c("2021-2025", "2017-2021", "2013-2017", "2009-2013", 
                   "2005-2009", "2001-2005", "1997-2001", "1993-97"))

j <- list()

for (x in periods_storting$id) {
  j[[x]] <- get_parlperiod_mps(periodid = x, substitute = TRUE, 
                               good_manners = 0)
}


allmps <- do.call("rbind", j)

save(allmps, file = "data/mpdata.Rdata")

allmpsparties <- allmps %>% 
  select(question_from_id = mp_id, firstname, lastname, 
         gender, party_id, county_id, period_id)

```

The issue is that the questions themselves are structured around sessions and id from them, while the MPs are related to a period id. So we need to assign all questions a relevant period_id as well, so we can join them together with information regarding the MPs who actually asked the question. 

```{r}
questiontext <- questiontext %>%
  mutate(period_id = case_when(session_id == "2021-2022" ~ "2021-2025",
                               session_id == "2020-2021" ~ "2017-2021",
                               session_id == "2019-2020" ~ "2017-2021",
                               session_id == "2018-2019" ~ "2017-2021",
                               session_id == "2017-2018" ~ "2017-2021",
                               session_id == "2016-2017" ~ "2013-2017",
                               session_id == "2015-2016" ~ "2013-2017",
                               session_id == "2014-2015" ~ "2013-2017",
                               session_id == "2013-2014" ~ "2013-2017",
                               session_id == "2012-2013" ~ "2009-2013",
                               session_id == "2011-2012" ~ "2009-2013",
                               session_id == "2010-2011" ~ "2009-2013",
                               session_id == "2009-2010" ~ "2009-2013",
                               session_id == "2008-2009" ~ "2005-2009",
                               session_id == "2007-2008" ~ "2005-2009",
                               session_id == "2006-2007" ~ "2005-2009",
                               session_id == "2005-2006" ~ "2005-2009",
                               session_id == "2004-2005" ~ "2001-2005",
                               session_id == "2003-2004" ~ "2001-2005",
                               session_id == "2002-2003" ~ "2001-2005",
                               session_id == "2001-2002" ~ "2001-2005",
                               session_id == "2000-2001" ~ "1997-2001",
                               session_id == "1999-2000" ~ "1997-2001",
                               session_id == "1998-99" ~ "1997-2001",
                               session_id == "1997-98" ~ "1997-2001", 
                               session_id == "1996-97" ~ "1993-1997"))

table(questiontext$session_id, questiontext$period_id)
```

Table tells us that this code has succesfully added a session to the questiontext data. Next step is joining the dataframe on individual MPs data with the complete set. Previously I considerably reduced the dataset itself in order to only pull out relevant information. 

```{r}

df <- left_join(questiontext, allmpsparties, by = c("question_from_id", "period_id"))

save(df, file = "data/usedata.Rdata")

```

The df dataframe represents the usable dataframe, while questionmeta can still be called on if details are needed. The reason we want to use the entire dataframe is to map out a topic model, and to do this we want as many observations to train the model on as possible. 


### Give a short description on how you captured the data and how they are structured

In the above script I have hopefully probably illustrated how the data was collected. The data itself does not represent the 